### 2022-06-15 manuscript.tex
Merge pull request #239 from SORTEE-Github-Hackathon/RCO-author-credit [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/4ac5f7eeaa29350c0b737ed7e3e45fa0be45da12.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/4ac5f7eeaa29350c0b737ed7e3e45fa0be45da12/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2505155697

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/8c2aac108bf451c48272ca35f8bd93bfd6a499fd/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/8c2aac108bf451c48272ca35f8bd93bfd6a499fd}{SORTEE-Github-Hackathon/manuscript@8c2aac1}
on June 13, 2022.

@@

@@

This manuscript arose from a hackathon at the Society for Open, Reliable, and Transparent Ecology and Evolution (SORTEE) virtual meeting in July 2021.

@@

The source code and data for this manuscript are available at https://github.com/SORTEE-Github-Hackathon/manuscript.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/4ac5f7eeaa29350c0b737ed7e3e45fa0be45da12/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/4ac5f7eeaa29350c0b737ed7e3e45fa0be45da12}{SORTEE-Github-Hackathon/manuscript@4ac5f7e}
on June 15, 2022.

@@

\hypertarget{author-contributions}{%
\subsection{Author Contributions}\label{author-contributions}}

We indicate author contributions using the \href{https://casrai.org/credit/}{CRediT Taxonomy}
Conceptualization: RCO, BPME, KH, EJH, LLSR, PHPB
Investigation: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
Methodology: RCO, BPME, KH, EJH, LLSR, PHPB
Project administration: RCO

Software: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
Visualization: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
Writing -- original draft: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
Writing -- review \& editing: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB

@@

This manuscript arose from a hackathon at the Society for Open, Reliable, and Transparent Ecology and Evolution (SORTEE) virtual meeting in July 2021. We thank Ciera Martinez for being a co-organizer of the SORTEE hackathon that started our discussion on GitHub in EEB and for creating our hackathon website on GitHub.

@@

The source code and data for this manuscript are available at https://github.com/SORTEE-Github-Hackathon/manuscript. The source code will be archived in the ESS-DIVE data repository prior to publication.
